---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gao

<!-- badges: start -->
<!-- badges: end -->

`gao` provides tools for harvesting reports published by the United States
Government Accountability Office (GAO). It ships with a bundled dataset of
all GAO report URLs (updated daily via GitHub Actions) and functions for
downloading reports as PDF or HTML files.

**Disclaimer:** This package is not affiliated with, endorsed by, or in any
way officially connected to the U.S. Government Accountability Office. "GAO"
refers to the publicly available reports hosted at
[gao.gov](https://www.gao.gov). All data is obtained from public web pages.

## Installation

`gao` requires [curl-impersonate](https://github.com/lexiforest/curl-impersonate)
as a system dependency (GAO.gov uses TLS fingerprint filtering that blocks
standard HTTP clients).

```bash
# Arch Linux
sudo pacman -S curl-impersonate

# macOS
brew install lexiforest/curl-impersonate/curl-impersonate
```

Then install the package from GitHub:

```r
# install.packages("pak")
pak::pak("CetiAlphaFive/gao")
```

## Quick start

```{r, eval = FALSE}
library(gao)

# Interactive — prompts for format and year range
auto_download()

# Or specify everything up front
auto_download(format = "pdf", year = 2020:2024, confirm = FALSE)
```

`auto_download()` loads the bundled dataset of ~55,000 GAO report URLs, filters
by fiscal year, and downloads PDFs, HTMLs, or both into `gao_reports/pdf/` and
`gao_reports/html/`. That's it.

## Advanced usage

The functions below give you finer control over each step. Most users won't
need them.

### Browse the bundled dataset

```{r, eval = FALSE}
links <- gao_links()
length(links)
head(links)
```

### Update the link list

Fetch any reports published since the last package update:

```{r, eval = FALSE}
all_links <- update_links()
```

### Extract PDF download links

```{r, eval = FALSE}
pdf_links <- extract_pdf_links(links[1:10])
```

### Download reports

Download as PDFs:

```{r, eval = FALSE}
download_pdfs(pdf_links, download_dir = "gao_pdfs")
```

Or download report pages as HTML:

```{r, eval = FALSE}
download_htmls(links[1:10], target_directory = "gao_htmls")
```

### Full pipeline from scratch

If you need to re-scrape the entire report listing (not usually necessary):

```{r, eval = FALSE}
links <- extract_links(save_to_file = FALSE)
```

## License

MIT
