---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gao

<!-- badges: start -->
<!-- badges: end -->

`gao` automates the harvesting and downloading of reports published by the
United States Government Accountability Office (GAO). It provides functions for
scraping report page URLs, extracting PDF download links, and downloading report
files in PDF or HTML format using parallel processing.

## Installation

You can install the development version of gao from
[GitHub](https://github.com/CetiAlphaFive/gao) with:

```r
# install.packages("pak")
pak::pak("CetiAlphaFive/gao")
```

## Usage

The package provides a three-step pipeline for harvesting GAO reports:

### 1. Scrape report page URLs

```{r, eval = FALSE}
library(gao)

# Scrape all report page links from the GAO website
links <- extract_links(use_multicore = TRUE, workers = 4)
```

### 2. Extract PDF download links

```{r, eval = FALSE}
# Extract the actual PDF download links from each report page
pdf_links <- extract_pdf_links(links, workers = 4)
```

### 3. Download reports

Download as PDFs:

```{r, eval = FALSE}
download_pdfs(pdf_links, download_dir = "gao_pdfs", workers = 4)
```

Or download as HTML:

```{r, eval = FALSE}
download_htmls(links, target_directory = "gao_htmls", workers = 4)
```
