---
title: "Downloading reports and extracting text"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

Browsing the metadata needs nothing beyond the package itself. This
article covers the next step: downloading the actual report files in
bulk and turning them into analyzable text.

## One-time setup: curl-impersonate

gao.gov's servers reject requests from ordinary download tools, so the
package uses [curl-impersonate](https://github.com/lexiforest/curl-impersonate),
a variant of curl that gao.gov accepts. Install it once:

```bash
# Arch Linux
sudo pacman -S curl-impersonate

# macOS
brew install lexiforest/curl-impersonate/curl-impersonate
```

For other platforms, prebuilt binaries are available from the
[curl-impersonate releases page](https://github.com/lexiforest/curl-impersonate/releases).
If the binary has a different name or location on your system, point the
package at it with
`options(gao.curl_bin = "/path/to/curl_firefox147")`.

Everything else in the package works without it, and any function that
needs it will remind you with these instructions.

## Downloading reports

`auto_download()` is the one-stop function. Called with no arguments in
an interactive session, it walks you through the choices --- format,
year range, and a confirmation with the total file count before anything
is downloaded:

```{r}
library(gao)

auto_download()
```

Or specify everything up front, for scripts:

```{r}
# All reports from fiscal years 2023-2024, as PDF
auto_download(format = "pdf", year = 2023:2024, confirm = FALSE)
```

Files land in your working directory:

```
gao_reports/
├── pdf/
│   ├── gao-23-105043.pdf
│   ├── gao-23-105177.pdf
│   └── ...
└── html/        (with format = "html" or "both")
```

Downloads pause for one second between files (adjustable via
`sleep_time`) to be polite to gao.gov. A full fiscal year is typically a
few hundred reports, so plan for several minutes per year and a few
hundred MB of disk space.

### Metadata only, no downloads

`format = "metadata"` skips the downloads entirely and writes the
filtered metadata to a CSV --- useful when you only need the report list
in a spreadsheet or another language:

```{r}
auto_download(format = "metadata", year = 2020:2024, confirm = FALSE)
```

## Extracting text

Once you have PDFs, `extract_text()` reads a whole directory into a
data.frame --- one row per file, with the full text of all pages in one
string. It requires the `pdftools` package
(`install.packages("pdftools")`).

```{r}
texts <- extract_text("gao_reports/pdf")

nrow(texts)          # one row per PDF
texts$file[1]        # the filename
texts$pages[1]       # its page count
substr(texts$text[1], 1, 200)  # the first 200 characters of text
```

From here you are ready for standard text-analysis tools --- for
example, counting term mentions across reports:

```{r}
mentions <- grepl("climate change", texts$text, ignore.case = TRUE)
sum(mentions)
```

Very old reports are scanned images rather than digital text; those
yield `NA` text (with a warning listing the affected files), so filter
with `is.na(texts$text)` before analysis.

## Joining text back to metadata

Filenames follow the report URL slug, so you can connect extracted text
back to the metadata in `gao_links()`:

```{r}
reports <- gao_links()
reports$file <- paste0(basename(reports$url), ".pdf")

full <- merge(texts, reports, by = "file")
```

Now every report's text sits alongside its topics, agencies, requesters,
and the rest of the metadata --- ready for whatever question you are
asking.
