---
title: "The GAO report dataset"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4.5
)
```

The heart of the `gao` package is a dataset covering every product the
U.S. Government Accountability Office has published since 1921 ---
reports, testimonies, correspondence, and legal decisions. This article
walks through what is in it and how to work with it.

## Loading the data

The dataset ships with the package, so this works offline:

```{r, message = FALSE}
library(gao)

reports <- gao_links()
dim(reports)
```

One row per GAO product. Here is a recent slice:

```{r}
subset(reports, pub_fiscal_year == 2025,
       select = c(report_id, published, title)) |>
  head(3)
```

## The columns, in three groups

### 1. Core metadata

What GAO publishes about each report: `title`, `summary`, `published`
and `released` dates, `page_count`, `topics`, `subject_terms`, the
`agencies_affected`, how many recommendations it makes
(`n_recommendations`), and who asked for it (`requester_type`,
`requester_committees`, `requester_members`).

```{r}
one <- subset(reports, report_id == "GAO-24-105891")
one$title
one$topics
one$agencies_affected
one$n_recommendations
```

### 2. Indicator columns

Fields like `topics` pack several values into one semicolon-separated
string, which is awkward to filter on. So the dataset also includes
ready-made 0/1 indicator columns: 31 `topic_*` columns and 50 `agency_*`
columns (plus `agency_other`) for the most frequently reviewed agencies.

```{r}
# Defense-related reports affecting the Department of Veterans Affairs
subset(reports,
       topic_national_defense == 1 &
         agency_department_of_veterans_affairs == 1,
       select = c(report_id, published, title)) |>
  head(3)
```

Indicators are `NA` (not 0) when the underlying field is missing, which
is common for older reports.

### 3. Derived covariates

Columns computed from the metadata that are handy for analysis:

- `product_type` --- what kind of product this is:

```{r}
table(reports$product_type)
```

- `pub_fiscal_year`, `fiscal_quarter`, `pub_month`, `pub_dow`,
  `election_year`, `release_lag_days` --- timing covariates (federal
  fiscal years start in October).
- `issuing_division` --- the GAO unit that produced the report, decoded
  from older report IDs.
- `n_topics`, `n_subject_terms` --- how broad the report is.
- `requester_party`, `requester_chamber`,
  `requester_majority_status`, `requester_bipartisan` --- who in
  Congress requested the report, resolved against
  [Voteview](https://voteview.com/) membership data. These are only
  populated for reports that name individual members as requesters:

```{r}
table(reports$requester_party)
```

## A quick look at the whole library

```{r reports-per-year}
counts <- table(reports$pub_fiscal_year)
plot(as.integer(names(counts)), as.integer(counts), type = "h",
     xlab = "Fiscal year", ylab = "Reports published",
     main = "GAO products per fiscal year, 1922-present")
```

## A note on missing values

GAO's own pages are sparser for older material, so expect more `NA`s as
you go back in time: summaries, topics, and requester fields are richest
from the 1970s onward, and page counts exist only where a PDF is
available. Always check `is.na()` before filtering on these columns.

## Getting the newest data

The dataset is refreshed daily. To pick up the latest version without
reinstalling the package:

```{r, eval = FALSE}
gao_update_data()
```

This caches the new dataset locally, and `gao_links()` uses it
automatically from then on.
